---
title: "basic-usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{basic-usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
#library('GenoClustR')
devtools::load_all()
library('rlang')
library('ggplot2')
library("Hmisc")
library('gplots')
library("WGCNA")
enableWGCNAThreads()
```

```{r}
plotit <- function(mat) {
  heatmap(mat, Rowv = NA, Colv = NA, symm = TRUE)
}
```

```{r}
cor <- matrix(0, nrow = 200, ncol = 200)
diag(cor) <- 1

cor[5:15, 5:15] <- 1 # Clean separation

cor[20:25, 20:25] <- 1 # Non-overlapping but adjacent
cor[26:31, 26:31] <- 1

cor[36:41, 36:41] <- 1 # Small overlap
cor[41:46, 41:46] <- 1

cor[50:60, 50:60] <- 1 # Mid overlap
cor[55:65, 55:65] <- 1

cor[70:80, 70:80] <- 1 # Large overlap
cor[72:82, 72:82] <- 1

cor[85:95, 85:95] <- 1 # Small overlap big clusters
cor[95:105, 95:105] <- 1


set.seed(123)
# big and noisy :)
cor[107:117, 107:117] <- rbinom(11 ** 2, 1, 0.9)

cor[120:130, 120:130] <- rbinom(11 ** 2, 1, 0.8)

cor[135:145, 135:145] <- rbinom(11 ** 2, 1, 0.7)

cor[150:160, 150:160] <- rbinom(11 ** 2, 1, 0.6)

cor[165:175, 165:175] <- rbinom(11 ** 2, 1, 0.5)

cor[180:190, 180:190] <- rbinom(11 ** 2, 1, 0.4)

cor[195:200, 195:200] <- rbinom(6 ** 2, 1, 0.2)
cor[lower.tri(cor)] <- t(cor)[lower.tri(cor)]
diag(cor) <- 1

plotit(cor)

#data(sclero)

#cor <- abs(cor(t(sclero)))
#cor <- 1 * (cor > 0.7)

cor_tom <- TOMsimilarity(cor)
plotit(cor_tom)
#cor <- cor_tom
cor[1:10, 1:10]
```



So how does the thresholded pipeline do?

```{r}
threshold_clustering(cor, max_cluster = 50)$clusters
```

Pretty good actually.
The only one it didn't get right was the gappy cluster, which had the boundaries wrong.
Incidentally, this is the one that is most likely to have issues with the thresholding method.

Most of these examples are pretty easy, but they're the clear cases that any method should be able to deal with.

What if we use the WGCNA method for cleaning clusters instead?

```{r}
#threshold_clustering(cor, max_cluster = 50, smooth = "TOM")$clusters
```

It fails to merge the "mid overlap" cluster (it's debatable about whether this should be merged), but does better with the gappy cluster.
I think probably this is the more reliable method.


So what else can we do?

```{r}
## from http://tr.im/hH5A
logsumexp <- function (x) {
  y <- max(x)
  y + log(sum(exp(x - y)))
}

softmax <- function (x) {
  x <- x + min(x)
  exp(x - logsumexp(x))
}


unity <- function(xi, xj) {
  return(1)
}


rbf <- function(xi, xj, std = 1, power = 2) {
  ratio <- (abs(xi - xj) ** 2) / (2 * (std ** power))
  return(exp(-1 * ratio))
}

gen_pm_features <- function(mat, context = 3, dist_penalty = unity) {
  # p_rev, p_fwd, p_none
  out <- matrix(NA, nrow = nrow(mat), ncol = 4)
  for (i in seq_len(nrow(mat))) {
    fwd_ <- numeric(context)
    rev_ <- numeric(context)

    for (j in seq_len(context)) {
      if ((i + j) >  nrow(mat)) {
        f <- 0
      } else {
        f <- mat[i, (i + j)]
      }
      dp <- dist_penalty(1, j)
      
      fwd_[j] <- dp * f
      
      if ((i - j) <= 0) {
        r <- 0
      } else {
        r <- mat[i, (i - j)]
      }
      
      rev_[j] <- dp * r
    }

    fwd_ <- (fwd_ - 0.5) * 2
    rev_ <- (rev_ - 0.5) * 2

    both_ <- sum(c(fwd_, rev_), na.rm = FALSE)
    fwd2_ <- sum(c(fwd_, -1 * rev_), na.rm = FALSE)
    rev2_ <- sum(c(-1 * fwd_, rev_), na.rm = FALSE)
    neither_ <- sum(-1 * c(fwd_, rev_), na.rm = FALSE)
    
    out[i,] <- softmax(c(rev2_, fwd2_, both_, neither_))
  }
  colnames(out) <- c("rev", "fwd", "both", "neither")
  return(out)
}

heatmap(gen_pm_features(cor, context = 4), Rowv = NA, Colv = NA)

gen_pm_features(cor, context = 10, dist_penalty = function(xi, xj) {rbf(xi, xj, std = 2, power = 4)})
```

$transProbs
               to
from             nocluster cluster_start    cluster cluster_end
  nocluster     0.70503419    0.22859469 0.03284794  0.03352318
  cluster_start 0.03613480    0.64380925 0.21054008  0.10951588
  cluster       0.03959185    0.04893161 0.67604962  0.23542692
  cluster_end   0.24633205    0.06610597 0.04377526  0.64378672

```{r}
transition_table <- matrix(0, nrow = 4, ncol = 4)
rownames(transition_table) <- colnames(transition_table) <- states <- c("nocluster", "cluster_start", "cluster", "cluster_end")

transition_table["cluster_end", "nocluster"] <- 0.25
transition_table["nocluster", "nocluster"] <- 0.75

transition_table["cluster_start", "cluster"] <- 0.1
transition_table["cluster", "cluster"] <- 0.9

transition_table["cluster_start", "cluster_end"] <- 0.1
transition_table["cluster", "cluster_end"] <- 0.9

transition_table["cluster_end", "cluster_start"] <- 0.5
transition_table["nocluster", "cluster_start"] <- 0.5


heatmap(transition_table, Rowv = NA, Colv = NA)
```


$emissionProbs
               symbols
states                 rev        fwd       both    neither
  nocluster     0.04412888 0.04413120 0.03156040 0.88017952
  cluster_start 0.05257447 0.85767542 0.04419816 0.04555196
  cluster       0.08585462 0.08588891 0.78916555 0.03909092
  cluster_end   0.85825106 0.05263497 0.04423603 0.04487795

```{r}
start_table = matrix(0, nrow = 1, ncol = 4)
colnames(start_table) <- c("nocluster", "cluster_start", "cluster", "cluster_end")
start_table[1, ] <- c(0.99, 0.01, 0.0, 0.0)

emission_table <- matrix(0, nrow = 4, ncol = 4)
rownames(emission_table) <- c("nocluster", "cluster_start", "cluster", "cluster_end")
colnames(emission_table) <- symbols <- c("rev", "fwd", "both", "neither")
emission_table["cluster_start",] <- c(0.25, 0.45, 0.25, 0.05)
emission_table["cluster",] <- c(0.1, 0.1, 0.75, 0.05)
emission_table["cluster_end",] <- c(0.45, 0.25, 0.25, 0.05)
emission_table["nocluster",] <- c(0.05, 0.05, 0.05, 0.85)
heatmap(emission_table, Rowv = NA, Colv = NA)
```

```{r}
obs_pm <- gen_pm_features(cor, context = 6)
obs <- colnames(obs_pm)[apply(obs_pm, MARGIN = 1, FUN = which.max)]
```


```{r}
heatmap(obs_pm, Rowv = NA, Colv = NA)
```

```{r}
emission_table
```

```{r}
heatmap(t(obs_pm[1:10,]), Rowv = NA, Colv = NA, scale = "none")
heatmap(emissions[, 1:10], Rowv = NA, Colv = NA, scale = "none")
heatmap(emission_table[, obs[1:10]], Rowv = NA, Colv = NA, scale = "none")
```

```{r}
trellis <- matrix(0, nrow = length(states), ncol = length(obs))
rownames(trellis) <- states

pointers <- matrix(0, nrow = length(states), ncol = length(obs))
rownames(pointers) <- states
```

```{r}
# initial state
emission_table <- log(emission_table)
transition_table <- log(transition_table)
start_table <- log(start_table)
```


```{r}
weighted_obs <- function(obs, emission_table) {
  multiplied <- t(t(emission_table) + obs)
  
  # Taking exp is important because we're in log space
  weighted_score <- rowSums(exp(multiplied))
  
  # Convert back to log for stability
  return(log(weighted_score))
}

weighted_obs(log(obs_pm[1,]), emission_table)
```


```{r}
# initial state
emissions <- apply(
  log(obs_pm),
  MARGIN = 1,
  FUN = function(x) {weighted_obs(x, emission_table)}
)

#emissions <- emission_table[, obs]
emission_preds <- rownames(emissions)[apply(emissions, MARGIN = 2, FUN = which.max)]

trellis[, 1] <- t(start_table + emissions[, 1])

for (o in seq_len(ncol(trellis) - 1)) {
  o <- o + 1
  for (state in states) {
    k <- trellis[, o - 1] + transition_table[, state] + emissions[state, o]
    top <- names(which.max(k))
    trellis[state, o] <- k[top]
    pointers[state, o] <- top
  }
}
```


```{r}
best_state <- names(which.max(trellis[, ncol(trellis)]))
best_path <- character(ncol(trellis))

for (i in rev(seq_len(ncol(trellis)))) {
  best_path[i] <- best_state
  best_state <- pointers[best_state, i]
}
```


```{r}
min_cluster <- 5
ranges <- list()

h <- 1
last_start <- NULL
for (i in seq_along(best_path)) {
  state <- best_path[i]
  if (state == "cluster_start") {
    if (!is.null(last_start)) {
      stop("this shouldn't happen")
    }
    last_start <- i
  } else if (state == "cluster_end") {
    if (is.null(last_start)) {
      stop("this shouldn't happen")
    }
    
    if ((abs(last_start - i) + 1) >= min_cluster) {
      ranges[[h]] <- c("start" = last_start, "end" = i)
      h <- h + 1
    }
    last_start <- NULL
  } else if (!state %in% c("cluster", "nocluster")) {
    stop("This shouldn't happen")
  }
}

ranges <- do.call(rbind, ranges)
```


cor[5:15, 5:15] <- 1 # Clean separation
cor[20:25, 20:25] <- 1 # Non-overlapping but adjacent
cor[26:31, 26:31] <- 1
cor[36:41, 36:41] <- 1 # Small overlap
cor[41:46, 41:46] <- 1
cor[50:60, 50:60] <- 1 # Mid overlap
cor[55:65, 55:65] <- 1
cor[70:80, 70:80] <- 1 # Large overlap
cor[72:82, 72:82] <- 1
cor[85:95, 85:95] <- 1 # Small overlap big clusters
cor[95:105, 95:105]
cor[107:117, 107:117]
cor[120:130, 120:130]
cor[135:145, 135:145]
cor[150:160, 150:160]
cor[165:175, 165:175]
cor[180:190, 180:190]
cor[195:200, 195:200]


```{r}
ranges
```

5	15	0.9090909	0	1.0000000	11	0
20	25	0.8333333	0	1.0000000	6	0
26	31	0.8333333	0	1.0000000	6	0
36	41	0.8333333	0	1.0000000	6	0
41	46	0.8333333	0	1.0000000	6	0
50	65	0.8750000	0	0.9916667	16	0
70	82	0.9230769	0	1.0000000	13	0
85	95	0.9090909	0	1.0000000	11	0
95	105	0.9090909	0	1.0000000	11	0
107	117	0.8181818	1	0.9090909	11	0
140	145	0.8333333	0	1.0000000	6	0


```{r}
for (i in seq_len(nrow(ranges))) {
  context <- 5
  start <- max(c(ranges[i, "start"] - context, 1))
  end <- min(c(ranges[i, "end"] + context, nrow(cor)))

  heatmap(cor[start:end, start:end], Rowv = NA, Colv = NA, symm = TRUE)
}
```

```{r}
library(HMM)
tr <- exp(transition_table)
#rownames(tr) <- colnames(tr) <- NULL
em <- exp(emission_table)
#rownames(em) <- colnames(em) <- NULL
start <- exp(start_table[1, ])
#names(start) <- NA

hmm <- initHMM(states, symbols, start, transProbs = tr, emissionProbs = em)
hmm_bw <- baumWelch(hmm, obs, pseudoCount = 1)$hmm
```


```{r}
best_path <- viterbi(hmm, observation = obs)

min_cluster <- 5
ranges <- list()

h <- 1
last_start <- NULL
for (i in seq_along(best_path)) {
  state <- best_path[i]
  if (state == "cluster_start") {
    if (!is.null(last_start)) {
      stop("this shouldn't happen")
    }
    last_start <- i
  } else if (state == "cluster_end") {
    if (is.null(last_start)) {
      stop("this shouldn't happen")
    }
    
    if ((abs(last_start - i) + 1) >= min_cluster) {
      ranges[[h]] <- c("start" = last_start, "end" = i)
      h <- h + 1
    }
    last_start <- NULL
  } else if (!state %in% c("cluster", "nocluster")) {
    stop("This shouldn't happen")
  }
}

ranges <- do.call(rbind, ranges)
ranges
```



```{r}
best_path <- viterbi(hmm_bw, observation = obs)

min_cluster <- 5
ranges <- list()

h <- 1
last_start <- NULL
for (i in seq_along(best_path)) {
  state <- best_path[i]
  if (state == "cluster_start") {
    if (!is.null(last_start)) {
      stop("this shouldn't happen")
    }
    last_start <- i
  } else if (state == "cluster_end") {
    if (is.null(last_start)) {
      stop("this shouldn't happen")
    }
    
    if ((abs(last_start - i) + 1) >= min_cluster) {
      ranges[[h]] <- c("start" = last_start, "end" = i)
      h <- h + 1
    }
    last_start <- NULL
  } else if (!state %in% c("cluster", "nocluster")) {
    stop("This shouldn't happen")
  }
}

ranges <- do.call(rbind, ranges)
ranges
```
